Meta-analysis

### 2020-06-12 04_MetaAnalysis.Rmd
Update meta-analysis explaination and contrasts with the extra spray_management variable

According to the results of the omnibus test ($Q_M = 10.65, df = 4, p = 0.0308$) we can reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields[@Viechtbauer2010]. 
However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 3.2276; p = 0.0012$). 
The analysis shows there is still a considerable amount of residual heterogeneity ($Q_E = 5096.04, df = 125, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

When we compare these results to those of the linear mixed effect model there is little difference in the outcome.

```{r compare_meta&lmer}
lme_PM <-
   lmer(yi ~ spray_management + (spray_management |
                                    trial), data = slimmer_PM_dat)

summary(lme_PM)
```

@@

To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
```{r metafor_contrasts}
anova(PM_mv_AI, L = rbind(
   c(0, 1, -1, 0, 0),
   # early vs Recommended
   c(0, 1, 0, -1, 0),
   # early vs recommended plus
   c(0, 1, 0, 0, -1),
   # early vs Late plus
   c(0, 0, -1, 1, 0),
   # Recommended plus vs recommended
   c(0, 0, -1, 0, 1),
   # Late_Plus vs Recommended
   c(0, 0, 0, -1, 1)
)) # Late_plus vs Recommended plus
```
Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields. Also the model was almost significant when assessing recommended_plus as saving more yield than recommended. This is probably due to the fact there were more comparisons between these two treatments which allowed a more certain outcome.
Let's view these comparisons in a plot.

@@

efficacy <- tbl_df(results_AI)
efficacy$Treatment <-
   factor(
      c(
         "control",
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late_plus"
      )
   )

@@

What is interesting here is that the variance in the control has increased while the treatments have decreased. This is despite the control being the best represented across all experiments. However it could also be because it also has a low number of pooled reps per trial. Let's look at how well each of the number treatments compare to each other. We can use the netmeta package to give a graphical representation of this.

@@

```{r netmeta-forest}
# I don't know why this is not working I will need to follow up on this
forest(
   net_con,
   reference.group = 4,
   rightcols = c("effect", "ci", "Pscore"),
   rightlabs = "P-Score",
   small.values = "bad"
)

>>>>

According to the results of the omnibus test ($Q_M = 7.32, df = 5, p = 0.1979$) we can't reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields [@Viechtbauer2010]. 
However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 2.598; p = 0.0094$). 
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 538.26, df = 141, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

@@

To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
```{r metafor_contrasts}
meta_cont <- anova(PM_mv_AI, L = rbind(
   c(0, 1, -1, 0, 0,0),
   # early vs Recommended
   c(0, 1, 0, -1, 0,0),
   # early vs recommended plus
   c(0, 1, 0, 0, -1,0),
   # early vs Late 
   c(0, 1, 0, 0, 0,-1),
   # early vs Late plus
   c(0, 0, -1, 1, 0,0),
   # Recommended plus vs recommended
   c(0, 0, -1, 0, 1,0),
   # Late  vs Recommended
   c(0, 0, -1, 0, 0,1),
   # Late_plus  vs Recommended
   c(0, 0, 0, -1, 1,0),
   # Late vs Recommended plus
   c(0, 0, 0, -1, 0,1),
   # Late_plus  vs Recommended plus
   c(0, 0, 0, 0, -1,1)
)) # Late vs Late_plus

change_labels <- function(x1){
   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
   x1
}

data.frame(contrasts = change_labels(meta_cont$hyp[,1]),
      estimates = meta_cont$Lb,
      se = meta_cont$se,
      z_val = meta_cont$zval,
      pval = meta_cont$pval)
```
Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields. Also the model was almost significant when assessing `Late_plus` as saving more yield than `Recommended`. This is probably due to the fact there were more comparisons between these two treatments which allowed a more certain outcome.
Let's view these comparisons in a plot.

@@

efficacy <- tbl_df(results_AI)
efficacy$Treatment <-
   factor(
      c(
         "control",
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   )

@@

Let's look at how well each of the number treatments compare to each other. We can use the netmeta package to give a graphical representation of this.

@@

```{r netmeta-forest}
# I don't know why this is not working I will need to follow up on this
forest(
   net_con,
   reference.group = 5,
   rightcols = c("effect", "ci", "Pscore"),
   rightlabs = "P-Score",
   small.values = "bad"
)
